A Study of Common Bug Fix Patterns in Rust \thanks{Competing Interests: We have no competing interests and are funded by a Discovery Grant from Canada's Natural Science and Engineering Research Council.}

### 2023-06-04 related.tex
grammar

>>>>

\subsection{Refactoring tools for Rust}
Clippy is a widely known as the best code refactoring tool for Rust. It can identify over 600 common mistakes and offer automated fixes. It provides users with the flexibility to adjust the linting level, allowing them to control the number of lint suggestions they receive. As discussed in Section~\ref{sec:bc_patterns}, we found that Clippy can detect and address five of our borrow-checker-related patterns. \cite{sam2017automated} introduced a refactoring tool that uses the Rust compiler infrastructure to perform various refactoring operations, including renaming variables, arguments, fields, functions, methods, structs, and enumerations, as well as inlining local variables, and reifying and eliding lifetime parameters. In a more advanced use case, \cite{ling2022rust} proposed CRustS, a tool designed for refactoring C2Rust output. C2Rust is a C to Rust transpiler that converts C code into Rust syntax but retains the unsafe semantics of C. By relaxing the constraint of preserving semantics during transformations, CRustS increases the proportion of transformed code that successfully passes the safety checks of the Rust compiler.

### 2023-06-04 results.tex
grammar

The concept of attributes in Rust is similar to Python's decorators and Java's annotations (though Java annotations may be less likely to have runtime effect; for instance, Java @Override adds additional compile-time constraints). While each language may have its own syntax and specific use cases, the fundamental idea of attaching additional information to code elements is shared across these languages. We describe bug patterns that involve modification in Attributes. In the case of Python, according to the findings of \cite{yang2022mining}, no bug patterns involving Python's decorators were reported in their study. \\

>>>>

The concept of attributes in Rust is similar to Python's decorators and Java's annotations (though Java annotations may be less likely to have runtime effect; for instance, Java @Override adds additional compile-time constraints). While each language may have its own syntax and specific use cases, the fundamental idea of attaching additional information to code elements is shared across these languages. We describe bug patterns that involve modification in Attributes. \cite{yang2022mining} found that their Python dataset included no bug patterns involving Python's decorators, in contrast to our findings about Rust changes.
